A pipeline to analyse time-course gene expression data

### 2019-10-29 scripts/manuscript.Rmd
Checking out histogram of scores and everything

@@

```{r visualize_scores_all_figure, fig.height=6, fix.width=6}
# Get the best score for each gene
scores = apply(scores_and_labels$scores, 1, min)
hist(scores, breaks=(1:50/50), col="black", main="Distribution of scores")
```

>>>>

The manuscript was last compile on `r Sys.time()`.

@@

```{r visualize_scores_all_figure, fig.height=6, fix.width=6}
# Get the best score for each gene
scores = apply(scores_and_labels$scores, 1, min)
hist(scores, breaks=(1:50/50)            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
            188745       low 6-RSEC.s singlece  R    9:50:32      1 scf-sm11
, col="black", main="Distribution of scores")
```
